Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms} \footnote{Lecture is based upon the materials provided by MSB~\cite{msb_metodstod} and previous lectures written by Carina Bengtsson and Daniel Bosk}.

### 2019-04-02 msbframework/msbintro/msbintro.tex
Missed one heading
Moved another slide to improve the structure
Moved the footnote in the title page

\title[Intro infosäk]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.
}
\author{Lennart Franked\footnote{Lecture is based upon the materials provided by
  MSB~\cite{msb_metodstod} and previous lectures written by Carina Bengtsson and
  Daniel Bosk}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.
}

@@

\begin{frame}{What is information security?}
  \begin{figure}
    \includegraphics[height=0.7\textheight]{Figures/infosak-struktur.png}
    \caption{Structure of information security.}
  \end{figure}
\end{frame}

>>>>

\title[Intro infosäk]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for
  introducing \ac{isms}
  \footnote{Lecture is based upon the materials provided by
    MSB~\cite{msb_metodstod} and previous lectures written by Carina Bengtsson
    and Daniel Bosk}.
}
\author{Lennart Franked}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.
}

@@

\begin{frame}{Structure}{What is information security?}
  \begin{figure}
    \includegraphics[height=0.7\textheight]{Figures/infosak-struktur.png}
    \caption{Structure of information security.}
  \end{figure}
\end{frame}
